\documentclass[11pt]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlist[itemize]{noitemsep, topsep=2pt, leftmargin=*}

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\titlerule]
\titlespacing*{\section}{0pt}{10pt}{6pt}

\begin{document}

% ---------- Header ----------
{\LARGE \textbf{David Onyango Owuor}}\\
\href{mailto:david.owuor@ndsu.edu}{david.owuor@ndsu.edu} \,|\, 
\href{https://www.linkedin.com/in/david-owuor-082750201/}{LinkedIn} \,|\, 
\href{https://github.com/DMasilva}{GitHub: DMasilva}

% ---------- Summary ----------
\section*{Professional Summary}
Software developer with experience building web applications and internal tools using React, TypeScript, Ruby on Rails, and SQL. Comfortable working across the stack, debugging issues, integrating APIs, and supporting testing and deployments. Strong foundation in data reporting (PowerBI) and user-focused problem solving, with experience working in team environments and documenting technical work.

% ---------- Skills ----------
\section*{Technical Skills}
\textbf{Languages:} TypeScript, JavaScript, Python, Java, Ruby, SQL, HTML/CSS \\
\textbf{Frontend:} React, Tailwind CSS, Bootstrap \\
\textbf{Backend:} Ruby on Rails, Node.js, FastAPI, REST APIs \\
\textbf{Testing:} JUnit (basic), Debugging, Validation/Smoke Testing \\
\textbf{Data \& Reporting:} PowerBI, Tableau (basic) \\
\textbf{Tools:} Git, Docker, VS Code, Visual Studio, IntelliJ, Eclipse \\
\textbf{Platforms:} Microsoft 365, Google Workspace (collaboration/documentation)

% ---------- Experience ----------
\section*{Experience}

\textbf{Full Stack Developer Intern} \hfill Mar 2025 -- Present\\
Pavewise Pro — Fargo, ND
\begin{itemize}
  \item Built and maintained application features using React and TypeScript; supported backend development using Ruby on Rails.
  \item Worked with APIs and data flows to support internal tooling and reporting needs.
  \item Developed dashboards and operational reporting using PowerBI and JavaScript-based data processing where needed.
  \item Debugged issues, supported testing and validation, and contributed to deployment-related tasks.
  \item Collaborated with team members using clear documentation and structured handoffs.
\end{itemize}

\textbf{Front-end Web Developer Intern} \hfill Feb 2023 -- Aug 2023\\
TIENDA Logistics — Nairobi, KE
\begin{itemize}
  \item Developed responsive UI components using React, HTML, CSS, and JavaScript.
  \item Integrated REST APIs and tested UI behavior across browsers and devices.
  \item Documented UI components and patterns to support maintainability.
\end{itemize}

\textbf{Graduate Student Technology Assistant} \hfill Aug 2023 -- Nov 2024\\
Instruction Design Center, IT Division — NDSU, ND
\begin{itemize}
  \item Built documentation and training materials that improved adoption of campus platforms and reduced repeated support issues.
  \item Supported technology transitions and basic testing/validation during platform updates.
  \item Used reporting tools to track trends and communicate findings to the support team.
\end{itemize}

\textbf{IDC Student Supervisor} \hfill Nov 2024 -- Dec 2025\\
Instruction Design Center, IT Division — NDSU, ND
\begin{itemize}
  \item Led a small student team; improved workflows through documentation, troubleshooting playbooks, and process cleanup.
  \item Managed and resolved issues using a ticketing workflow; tracked recurring problems and shared recommendations.
  \item Coordinated with IT teams and stakeholders to support platform updates and user needs.
\end{itemize}

\textbf{IT Assistant} \hfill Dec 2020 -- Jul 2022\\
Solar Rays Energy Sacco — Nairobi, KE
\begin{itemize}
  \item Supported systems and end users; performed troubleshooting, updates, and maintenance on user machines and software.
  \item Maintained documentation and produced basic reports to support operations.
\end{itemize}

% ---------- Projects ----------
\section*{Projects}

\textbf{Theater Tours and Travels} \hfill Feb 2024 -- Aug 2024\\
Java, React, SQL, Tailwind CSS
\begin{itemize}
  \item Built a tours and travel booking system with a responsive frontend and database-backed features.
  \item Implemented core booking workflows and UI pages; integrated data storage and retrieval.
\end{itemize}

\textbf{Moringa Application Portal} \hfill Oct 2022 -- Jun 2023\\
React, Ruby on Rails
\begin{itemize}
  \item Developed a full-stack admissions management system supporting application intake and review workflows.
  \item Implemented frontend forms and backend logic; improved reliability through debugging and iteration.
\end{itemize}

\textbf{Cloud Support Dashboards} \hfill Mar 2024 -- Jun 2024\\
PowerBI, FreshService Data
\begin{itemize}
  \item Built dashboards to visualize FreshService trends and service health; improved visibility into workload and recurring issues.
\end{itemize}

\textbf{Hybrid Approach to Software Testing (Research)} \hfill May 2024 -- Present\\
Java, Maven, Python, GPT-based Models
\begin{itemize}
  \item Research on combining LLMs with traditional testing tools to improve test coverage and efficiency.
\end{itemize}

% ---------- Education ----------
\section*{Education}

\textbf{North Dakota State University}, Fargo, ND \hfill Aug 2023 -- Dec 2025\\
Master of Computer Science

\textbf{Technical University of Kenya}, Nairobi, KE \hfill Sep 2016 -- Nov 2020\\
Bachelor of Science, Information Science

\textbf{Moringa School and Flatiron School}, Nairobi, KE \hfill Nov 2022 -- Jun 2023\\
Certificate in Software Development

% ---------- Additional ----------
\section*{Additional}
Strong communication and documentation skills; experience working with users and stakeholders; comfortable learning new tools quickly and working in collaborative environments.

\end{document}
